\papertitle

### 2014-03-18 final-report/paper.tex
more intro

In particular, \system is built to inspect query execution in Myria\footnote{\url{http://myria.cs.washington.edu/}}, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.

The proposed visualizations can easily be applied to other DDBMS as well (e.g. Spark, Hadoop).

@@

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze.

>>>>

In particular, \system is built to inspect query execution in Myria\footnote{\url{http://myria.cs.washington.edu/}}, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.
The proposed visualizations can easily be applied to other DDBMS as well (e.g. Spark, Hadoop).

@@

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool
is called \system, which uses profiling logs from Myria \cite{myria} as the prototype DDMS. Myria is a distributed 
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently
